Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-04-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-short-body.tex
Revises conclusions

In concordance with the results obtained in other 
browser-based volunteer systems, after 
applying the gamification techniques, user participation was increased.

One of the interesting future lines of work would be to look a bit
more closely at the behavior of users as they are rating artifacts 
in the web system. These initial experiments hint at a possible power law, which might indicate that
the IEC system could be self-organizing, a process that would allow it
to reach a critical state, as has been found in software repositories,
for instance \cite{Merelo2016:repomining}.

One of the interesting future lines of work would be to study the possible negative effects of using  
gamification techniques to improve engagement, like cheating or
literally {\em gaming} the system to defeat competition. 
Finally, the refinement of the proposed Human-Centered framework will need
more case studies and further multi-disciplinary research.

>>>>

In concordance with the results obtained in other 
browser-based volunteer systems, after 
applying the gamification techniques, user participation was
increased. By the nature of the experiment, we will have to repeat it
several times and check causal correlation, but in general all
measurements indicate that is the case.

One of the interesting future lines of work would be to look a bit
more closely at the behavior of users as they are rating artifacts 
in the web system. These initial experiments hint at a possible power law, which might indicate that
the IEC system could be self-organizing, a process that would allow it
to reach a critical state, as has been found in software repositories,
for instance \cite{Merelo2016:repomining}. It would be also
interesting to study the possible negative effects of using   
gamification techniques to improve engagement, like cheating or
literally {\em gaming} the system to defeat competition. 
Finally, the refinement of the proposed Human-Centered framework will need
more case studies and further multi-disciplinary research.
